---
title: "The Global Impact of COVID19 (From February 24th, 2020 to February 23rd, 2021)"
author: "Elikplim Sabblah"
date: "2/22/2021"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document takes a statistical look at the effect that the COVID-19 pandemic has had on nations and human lives.
The data spans a one-year period and reveals so many different ways the pandemic has affected lives across the continents and countries of this world. 

### Visualizations

First, we would like to take a look at how much testing has been done on the various continents of the world. 

```{r include=FALSE}
COVID <- read_csv("C:/Users/PAS/Downloads/owid-covid-data (1).csv")
head(COVID)
```

```{r fig.height=8, fig.width=10, paged.print=TRUE}
COVID_tests <- COVID %>%
  select(continent, new_tests, tests_per_case)
COVID_tests1<- aggregate(cbind(new_tests, tests_per_case)~continent, COVID_tests, sum)

covid_Tests2 <- COVID_tests1 %>%
  gather(new_tests,tests_per_case, key = "Details", value = "Number")

ggplot(COVID_tests1, aes(continent, new_tests))+
  geom_bar(stat = "identity", fill = "red4") + 
  theme_bw()+
  geom_text(aes(label = new_tests), vjust = -0.4, size = 6)+ 
  theme(axis.text = element_text(size = 15, colour = "black", face = "bold"),
        axis.title = element_text(size = 15, face = "bold")) + 
  theme(plot.title = element_text(size = 20, face = "bold"))+
  labs(title = "Total Number of COVID19 Tests Done on Continents", x = "Continent", y = "Number of Tests")
  
```

Secondly, we would like to compare the number of tests done on all continents to the number of reported cases. 

```{r}
COVID_testcase <- COVID %>%
select(continent, new_tests, new_cases)
COVID_testcase1<- aggregate(cbind(new_tests, new_cases)~continent, COVID_testcase, sum)
ggplot(COVID_testcase1, aes(new_tests, new_cases, colour = continent)) + 
  geom_point(size = 4) + 
  theme_bw() + 
  scale_colour_manual(values = c("tomato2",  "red4", "lightsalmon4",
                               "violetred", "steelblue2", "skyblue4"))
  

```

Number of COVID Deaths vs Cardiovascular diseases related deaths
```{r}

```

